---
title: "Week 3 Assignment"
author: "Md Asadul Islam"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
library(tibble)
```

### 1. Normalization

Here I have three tables which demonstrate UNF, INF, 2NF and 3NF.

```{r code-chunk-label}
# Unnormalized Data (UNF)
unnormalized_data <- tibble(
  EmployeeID = c(1, 2, 3, 4),
  Name = c("Alice", "Bob", "Yvonne", "Emily"),
  Department = c("HR", "Finance", "IT", "Management"),
  Projects = c("Recruitment, Payroll", "Budgeting, Forecasting", "Software, database", "Commissioning, Opening"),
  Skills = c("Communication, Management", "Analysis, Excel", "Development, testing", "Resource, Planning")
)

print(unnormalized_data)

```

1NF
```{r chnuk code for 1NF}
# Data in First Normal form (1NF) 

first_normal_form <- tibble(
  EmployeeID = c(1, 1, 2, 2, 3, 3, 4, 4),
  Name = c("Alice", "Alice", "Bob", "Bob", "Yvonne", "Yvonne", "Emily", "Emily"),
  Department = c("HR", "HR", "Finance", "Finance", "IT", "IT", "Management", "Management"),
  Project = c("Recruitment", "Payroll", "Budgeting", "Forecasting", "Software", "Database", "Commissioning", "Opening"),
  Skill = c("Communication", "Management", "Analysis", "Excel", "Development", "Testing", "Resource", "Planning")
)

print(first_normal_form)



```

2NF

```{R chunk code for 2NF}

# Create Employee-Department table
employee_department <- tibble(
  EmployeeID = c(1, 2, 3, 4),
  Name = c("Alice", "Bob", "Yvonne", "Emily"),
  Department = c("HR", "Finance", "IT", "Management")
)

# Create Employee-Project table
employee_project <- tibble(
  EmployeeID = c(1, 1, 2, 2, 3, 3, 4, 4),
  Project = c("Recruitment", "Payroll", "Budgeting", "Forecasting", "Software", "Database", "Comissioning", "Opening")
)

# Create Employee-Skill table
employee_skill <- tibble(
  EmployeeID = c(1, 1, 2, 2, 3, 3, 4, 4),
  Skill = c("Communication", "Management", "Analysis", "Excel", "Development", "Testing", "Resource", "Planning")
)

print(employee_department)
print(employee_project)
print(employee_skill)

```
3NF
```{r chunk code for 3NF}
# Create Employee table
employee <- tibble(
  EmployeeID = c(1, 2, 3, 4),
  Name = c("Alice", "Bob", "Yvonne", "Emily")
)

# Create Department table
department <- tibble(
  EmployeeID = c(1, 2, 3, 4),
  Department = c("HR", "Finance", "IT", "Management")
)

# Create Project table
project <- tibble(
  EmployeeID = c(1, 1, 2, 2, 3, 3, 4, 4),
  Project = c("Recruitment", "Payroll", "Budgeting", "Forecasting", "Software", "Database", "Commissioning", "Opening")
)

# Create Skill table
skill <- tibble(
  EmployeeID = c(1, 1, 2, 2, 3, 3, 4, 4),
  Skill = c("Communication", "Management", "Analysis", "Excel", "Development", "Testing", "Resource", "Planning")
)

print(employee)
print(department)
print(project)
print(skill)


```

### 2. Character Manipulation

Identifying majors that contain either "DATA" or "STATISTICS"

```{r code chunk for identifying majors}

# Install and load necessary packages
library(dplyr)
library(stringr)

# Load the dataset from the url given
url <- "https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv"
majors_data <- read.csv(url)

# Display the first few rows of the dataset to understand its structure 
head(majors_data)

# Filter majors that contain either "DATA" or "STATISTICS" as requested
filtered_majors <- majors_data %>%
  filter(str_detect(Major, "DATA|STATISTICS"))

# Display the filtered majors based on the above criteria
print(filtered_majors)

```
### 3. Describe, in words, what these expressions will match:

(.)\1\1: This expression matches any character that appears three times in a row\n

"(.)(.)\\2\\1":  This expression matches a four-character string where the first two characters are mirrored by the second two characters in reverse order.\n

(..)\1: This expression matches any four-character string where the first two characters are repeated.\n

"(.).\\1.\\1": This expression matches any five-character string where the first, third, and fifth characters are the same, and the second and fourth characters can be any character.\n

"(.)(.)(.).*\\3\\2\\1" : This expression matches any string where three consecutive characters are followed somewhere later in the string (not necessarily immediately) by those three characters in reverse order.\n

### 4. Construct regular expressions to match words that:

Start and end with the same character: \n
^(.)\1.*\1$

Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.):\n
(\w\w).*\1

Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.):\n
(.*(.).*\2.*\2.*)

